School accessibility: a new index applied to enrollment and performance inequalities

### 2015-10-04 paper.Rmd
Various updates

---
title: 'School accessibility: a new index applied to enrollment and performance inequalities
  in Sao Paulo'
author: "Ana Moreno and Robin Lovelace"
output: pdf_document
bibliography: school-access-bib.bib
---

>>>>

---
title: 'School accessibility: a new index applied to enrollment and performance inequalities
  in Sao Paulo'
author: "Ana Moreno and Robin Lovelace"
output: word_document
bibliography: school-access-bib.bib
---
